Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-12 papers/ms.tex
update ms

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a refined
  view of open cluster dispersal.  Here we present an analysis of a
  group stars spanning Cepheus ($l=100^\circ$) to Hercules
  ($l=40^\circ$), hereafter the Cep-Her complex.
  The group includes four Kepler Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet is in a component of the Cep-Her
  complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.  Here we focus on the former three
  systems, which are in other regions of the association.  Based on
  kinematic evidence from Gaia, stellar rotation periods from TESS,
  and spectroscopy, these three systems are also $\approx$40 million
  years (Myr) old.  More specifically, we find that Kepler-1643 is
  $46^{+9}_{-7}$\,Myr old, based on its membership in a dense
  sub-cluster of the complex called RSG-5.  KOI-7368 and KOI-7913 are
  $36^{+10}_{-8}$\,Myr old, and are in a diffuse region that we call
  CH-2.  Based on the transit shapes and high resolution imaging, all
  three objects are most likely planets, with false positive
  probabilities of $6\times10^{-9}$, $4\times10^{-3}$, and
  $1\times10^{-4}$ for Kepler-1643, KOI-7368, and KOI-7913
  respectively.  These planets empirically demonstrate that
  mini-Neptunes with sizes of $\approx$2 Earth radii exist at ages of
  $\approx$40 million years.
\end{abstract}

@@

The discovery and characterization of transiting planets younger than
a billion years is a major frontier in current exoplanet research.
The reason is that the properties of young planets provide benchmarks
for studies of planetary evolution.  For instance, there are the
questions of when hot Jupiters arrive on their close-in orbits
\citep{dawson_johnson_2018}, how the sizes of planets with massive
gaseous envelopes evolve \citep{rizzuto_tess_2020}, when and if
close-in multiplanet systems fall out of resonance
\citep{arevalo_stability_2022,goldberg_architectures_2022}, and
whether and how mass-loss explains the radius valley
\citep{lopez_how_2012,Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018,lee_primordial_2021}.

The discovery of a young planet requires two claims to be fulfilled:
the planet must exist, and its age must be secured.  Spaced-based
photometry from K2 and TESS has yielded a number of young planets for
which the planetary evidence comes from transits, and the age is based
on either cluster membership
\citep{Mann_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,nardiello_pathosII_2020}
or else on correlates of youth such as stellar rotation, photospheric
lithium content, x-ray activity, or emission line strength
\citep{zhou_2021_tois,hedges_toi-2076_2021}.

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar groups \citep[{\it
e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.  To date these
analyses have mostly clustered on the stellar positions and 2-D
velocities measured by Gaia.  One important result is the discovery of
diffuse streams and tidal tails comparable in stellar mass to the
previously known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  Even
though these streams can be spread out over tens to hundreds of
parsecs, their velocity dispersions can remain coherent at the
$\sim$1\kms\ level.  They can also be much larger: as an extreme
example, internal dynamics and projection effects in the Hyades drive
stars in the tidal tails span up to $\pm 40\mkms$ in relative velocity
when projected against the cluster center \citep{jerabkova_800_2021}.
The stars in such diffuse regions can be verified to be the same age
as the core members ({\it i.e.}, coeval) through analyses of
color-absolute magnitude diagrams \citep{KounkelCovey2019}, stellar
rotation periods \citep{curtis_tess_2019,bouma_2021_ngc2516}, and
chemical abundances \citep{hawkins_2020}.  While there are many
implications for our understanding of star formation and cluster
evolution \citep{dinnbier_tidal_2020}, a separate consequence is that
we now know the ages of many more stars, including previously known
planet hosts.

@@

In this work, we expand on our previous study of a $38^{+7}_{-6}$ Myr
old Neptune-sized planet in the Kepler field (Kepler-1627~Ab;
\citealt{bouma_kep1627_2022}).  The age of this planet was derived
based on its host star's membership in the $\delta$\ Lyr\ cluster.
Our analysis of the cluster focused on the immediate spatial and
kinematic vicinity of Kepler-1627~A in order to secure the planet's
age.  However it became clear that the $\delta$\ Lyr\ cluster seems to
also be part of a much larger group of similarly aged stars.  This
group, which is at a distance of $\sim$330\,pc from the Sun, appears
to span Cepheus to Hercules (galactic longitudes, $l$, between
40$^\circ$ and 100$^\circ$), at galactic latitudes roughly between
0$^\circ$ and 20$^\circ$.  We therefore refer to it as the Cep-Her
complex.  It exhibits significant sub-structure over its $\approx$250
parsec length, and a detailed analysis of its memberships, kinematics,
and possible origin is currently being prepared by R.~Kerr and
collaborators.

Here, our focus is on the intersection of the Cep-Her complex with the
Kepler field.  Cross-matching the full set of candidate Cep-Her
members against known Kepler Objects of Interest (KOIs)
\citep{thompson_planetary_2018} yielded four candidate cluster
members: Kepler-1627, Kepler-1643, KOI-7368, and KOI-7913.  Given our
previous analysis of Kepler-1627, we will mostly focus on the latter
three.  After analyzing the relevant properties of Cep-Her
(Section~\ref{sec:cluster}), we derive the stellar properties
(Section~\ref{sec:stars}) and validate the planetary nature of each
system using a combination of the Kepler photometry and
high-resolution imaging (Section~\ref{sec:planets}).  We conclude with
a few caveats, and discuss implications for the size-evolution of
close-in mini-Neptunes (Section~\ref{sec:disc_conc}).

@@

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
Our fourth and final step was to cross-match the candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members
with weights exceeding 0.02, this yielded
 yielded 11 were known false positives, 6 ``confirmed'' planets, and 8
 ``candidate'' planets.  
Inspection of the Kepler data validation summaries and Robovetter
classifications for these objects showed whether they were
potentially consistent with being {\it i)} planets, and {\it ii)}
$\lesssim 10^8$ years old, based on the presence of rotational
modulation at the expected period and amplitude \citep[{\it
e.g.},][Figure~9]{rebull_rotation_2020}.  Four objects remained after
this inspection: Kepler-1627, Kepler-1643, KOI-7368, and
KOI-7913.\footnote{These figures
in fact give an estimate of the size of Cep-Her: if our 4/14
possible matches represent the true positive rate, then
multiplying by the number of stars above our weight threshold
(12{,}436) yields $\approx$3{,}500 stars in the complex.}

@@

We fitted the data as follows.  Given an initial guess for the transit
ephemeris from \citet{thompson_planetary_2018}, we first trimmed the
light curve to a local window around each transit that spanned three
transit durations before and after each mid-transit time.  The
out-of-transit points in each local window were then fitted with a
fourth-order polynomial, which was then divided out from the light
curve.  The resulting flattened transits were then fitted with a
planetary transit under the assumption of quadratic limb darkening.
Our model therefore included 8 free parameters for the transit ($\{P,
t_0, \log R_{\rm p}/R_\star, b, u_1 ,u_2, R_\star, \log g\}$), 2 free
parameters for the light curve normalization and a white noise jitter
($\{\langle f \rangle, \sigma_f \}$), and an additional 5 implicit
parameters for each transit.

@@

One weakness of our approach is that we have fixed 5 implicit
parameters per individual transit to their MAP values to remove the
stellar variability signal.  An alternative could be to fit the
planetary transits simultaneously with the starspot-induced
variability using, say, a quasiperiodic Gaussian process (GP).  We
explored this approach, but found that it required careful fine-tuning
of the hyperparameter priors, otherwise the GP would tend to
incorporate variability that was not part of the transit, even if it
was short-term variability attributable to flares or instrumental
noise.  This failure mode is pernicious, in that it yields an
ill-founded sense of confidence in an ``overly clean'' transit model
fit.  Our model is simpler, and it has the benefit that the white
noise jitter never trades off with any parameter equivalent to a
damping timescale for the coherence of the GP.  It is also
computationally efficient, and it captures the planetary parameters
about which we care the most.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		%    namelist = ['Kepler-1627 A', 'KOI-7368', 'KOI-7913 A', 'KOI-7913 B', 'Kepler-1643']
		%    markers = ['P', 'v', 'X', 'X', 's']
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
    3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
    its uncertainty. Kepler-1627 (+), KOI-7368 (down-triangle),
    KOI-7913 (X), Kepler-1643 (diamond).  The large sizes of the
    youngest transiting planets could be tied to a selection effect.
    Kepler-1643, KOI-7368, and KOI-7913 have normal mini-Neptune sizes
    of 2 to 3\,$R_\oplus$, which is a novelty given their ages.
    Parameters are from the NASA Exoplanet Archive (2022 Apr 5).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

The theoretical expectation is that mini-Neptunes with sizes of 2 to
3\,$R_\oplus$ should be common at ages of $10^7$ to $10^8$ years.
This expectation is tied to inferences about the
initial distributions of planetary core mass, core composition, and
atmospheric mass fraction \citep{owen_evaporation_2017}.  The
Kelvin-Helmholtz cooling timescale, which is tied to the entropy of
the planetary interior once the disk disperses, could also play a
significant role \citep{owen_constraining_2020}.  As an example,
\citet{rogers_unveiling_2021} predicted that given a core-mass
distribution peaked at $\approx$$4$\,M$_\oplus$, an ice-poor rock/iron
core composition, and a typical H/He mass fraction of $\approx$4\%,
there should be a maximum in planet occurrence at 2 to 3\,$R_\oplus$,
at times between 10 and 100\,Myr
(their Figure~16).  The models advanced by
\citet{gupta_signatures_2020} and \citet{lee_primordial_2021} agree;
the theoretical differences lie in their explanations
for the origin of the radius valley.  If the radius gap is primordial
and created by gas accretion physics, then super-Earths
($<$$1.8$\,$R_\oplus$) would be common as early as $10^7$ years
\citep{lee_primordial_2021}.   The photoevaporation-driven models more
often quote $10^8$ year timescales for production of
atmosphere-stripped super-Earths, while the models with the mass-loss
driven by a slow escape of heat from the core predict longer
$\sim$$10^9$ year timescales (but see \citealt{king_euv_2020}).

@@

From a data-driven perspective, demonstrating that a group of stars
was physically associated at its time of formation is challenging.
While some young groups show kinematic evidence for expansion
\citep{kuhn_kinematics_2019}, many, including Sco-Cen, do not
\citep{wright_kinematics_2018}.  This complicates the feasibility of
deriving kinematic ages through traceback, as
well as through the expansion itself
\citep[see][]{crundall_chronostar_2019}.  A more minimal approach is
that suggested by \citet{tofflemire_2021}: search for coeval,
phase-space neighbors, measure their ages, and determine if they share
a common age.  This approach can demonstrate whether a star is {\it
currently associated} with a set of coeval stars, which is much easier
than determining what the association looked like in the past.  Our
analysis of CH-2 meets the latter standard for the existence of a
$\approx$40\,Myr assocation today.  It would be a worthy exercise for
future work to perform a similar search for coeval phase-space
neighbors on the entire dataset of known exoplanet hosts.  For the
time being, we can offer the anecdotal point that in our experience,
most stars do not have dozens of $\sim$40\,Myr neighbors within a
local volume of a few \kms\ and tens of parsecs.

@@

\subsubsection{Cep-Her}
\paragraph{Kinematics}
* Need an RV survey.

\paragraph{Age(s)}
Benchmarking its age(s):
* Lithium analysis of FGK depletion (bright enough to be feasible).

* Asteroseismology of the delta Sct stars (TESS data are there, group is
rich enough).

\paragraph{More objects}

* TESS data: giant planets in Cep-Her.  We need more 1e7-1e8 year old
stars for the HJ occurrence versus time question.  This will help.

* Kepler data: exocomets?  Search for smaller planets?

\subsubsection{Occ rates}
* Kepler data... presumably $\sim$200 stars in the cluster were
observed, in order to have detected 4 planets. 
Occurrence rates?

@@

We have argued that Kepler-1643~b, KOI-7368~b, and KOI-7913~Ab {\it i)}
are 40 to 50 million years old, and {\it ii)} that each signal
is most likely planetary.  The evidence for the planetary
interpretation comes from an application of \texttt{VESPA} to the
Kepler data, alongside new adaptive optics imaging from NIRC2.  The
validity of the \texttt{VESPA} framework rests on the premise that
non-astrophysical false positives, including false alarms and known
neighboring eclipsing binaries, can be rejected.  Kepler-1643 and
KOI-7368 both pass all but one of the canonical vetting checks: the
check for centroid offsets between the in and out-of-transit phases.
For both cases, we have argued the weak observed shifts seem to be
caused by starspot-induced variability in specific quarters
shifting the stellar center-of-light.
In addition, our imaging rules out companions stars with the necessary
brightness and position to explain the reported shifts.

@@

The spatio-kinematic argument for the youth of KOI-7368 and
KOI-7913 is weaker because they are in an association of stars, CH-2,
that is more diffuse.  For KOI-7913, stronger indicators of its age
come from its binary.  Both stellar components in KOI-7913
have isochronal ages consistent with $40$\,Myr.
Both components also show H$\alpha$ in emission, which for
the $\approx$K6V primary is a good indicator that the star is
$\lesssim$100$\,$Myr old.  For KOI-7368, which is slightly more
massive, the Li 6708\AA\ EW measurement and stellar rotation period
are more constraining, and provide independent verification of the
star's youth.

>>>>

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a refined
  view of open cluster dispersal.  Here we present an analysis of a
  group stars spanning Cepheus ($l=100^\circ$) to Hercules
  ($l=40^\circ$), hereafter the Cep-Her complex.
  The group includes four Kepler Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet is in part of the Cep-Her
  complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.  Here we focus on the former three
  systems, which are in other regions of the association.  Based on
  kinematic evidence from Gaia, stellar rotation periods from TESS,
  and spectroscopy, these three objects are also $\approx$40 million
  years (Myr) old.  More specifically, we find that Kepler-1643 is
  $46^{+9}_{-7}$\,Myr old, based on its membership in a dense
  sub-cluster of the complex called RSG-5.  KOI-7368 and KOI-7913 are
  $36^{+10}_{-8}$\,Myr old, and are in a diffuse region that we call
  CH-2.  Based on the transit shapes and high resolution imaging, all
  three objects are most likely planets, with false positive
  probabilities of $6\times10^{-9}$, $4\times10^{-3}$, and
  $1\times10^{-4}$ for Kepler-1643, KOI-7368, and KOI-7913
  respectively.  These planets empirically demonstrate that
  mini-Neptunes with sizes of $\sim$2 Earth radii exist at ages of
  40 million years.
\end{abstract}

@@

The discovery and characterization of transiting planets younger than
a billion years is a major frontier in current exoplanet research.
The reason is that the properties of young planets provide benchmarks
for studies of planetary evolution.  For instance, young planets can
help inform our understanding
of when hot Jupiters arrive on their close-in orbits
\citep{dawson_johnson_2018}, how the sizes of planets with massive
gaseous envelopes evolve \citep{rizzuto_tess_2020}, when and if
close-in multiplanet systems fall out of resonance
\citep{arevalo_stability_2022,goldberg_architectures_2022}, and
whether and how mass-loss explains the radius valley
\citep{lopez_how_2012,Owen_Wu_2013,Fulton_et_al_2017,ginzburg_corepowered_2018,lee_primordial_2021}.

The discovery of a young planet requires two claims to be fulfilled:
the planet must exist, and its age must be secured.  Spaced-based
photometry from K2 and TESS has yielded a number of exemplars for
which the planetary evidence comes from transits, and the age is based
on either cluster membership
\citep{Mann_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,nardiello_pathosII_2020}
or else on correlates of youth such as stellar rotation, photospheric
lithium content, x-ray activity, or emission line strength
\citep{zhou_2021_tois,hedges_toi-2076_2021}.

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar groups \citep[{\it
e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.  To date these
analyses have mostly clustered on the stellar positions and 2-D
velocities.  One important result is the discovery of
diffuse streams and tidal tails comparable in stellar mass to the
previously known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  Even
though these streams are spread over tens to hundreds of
parsecs, their velocity dispersions can remain coherent at the
$\sim$1\kms\ level.  They can also be much larger: as an extreme
example, internal dynamics and projection effects in the Hyades drive
stars in the tidal tails to $\pm 40\mkms$ in relative velocity
when projected against the cluster center \citep{jerabkova_800_2021}.
The stars in such diffuse regions can be verified to be the same age
as the core members ({\it i.e.}, coeval) through analyses of
color-absolute magnitude diagrams \citep{KounkelCovey2019}, stellar
rotation periods \citep{curtis_tess_2019,bouma_2021_ngc2516}, and
chemical abundances \citep{hawkins_2020}.  While there are 
implications for our understanding of star formation and cluster
evolution \citep{dinnbier_tidal_2020}, a separate consequence is that
we now know the ages of many more stars, including previously known
planet hosts.

@@

In this work, we expand on our earlier study of a $38^{+7}_{-6}$ Myr
old Neptune-sized planet in the Kepler field (Kepler-1627~Ab;
\citealt{bouma_kep1627_2022}).  The age of this planet was derived
based on its host star's membership in the $\delta$\ Lyr\ cluster.
Our analysis of the cluster focused on the immediate vicinity of
Kepler-1627 in order to secure the planet's age.  However it became
clear that the $\delta$\ Lyr\ cluster seems to
also be part of a much larger group of similarly aged stars.  This
group, which is at a distance of $\sim$330\,pc from the Sun, 
spans Cepheus to Hercules (galactic longitudes, $l$, between
40$^\circ$ and 100$^\circ$), at galactic latitudes roughly between
0$^\circ$ and 20$^\circ$.  We therefore refer to it as the Cep-Her
complex.  It exhibits significant sub-structure over its $\approx$250
parsec length, and a detailed analysis of its memberships, kinematics,
and possible origin is currently being prepared by R.~Kerr and
collaborators.

Here, our focus is on the intersection of the Cep-Her complex with the
Kepler field.  Cross-matching our Cep-Her members against known Kepler
Objects of Interest (KOIs; \citealt{thompson_planetary_2018}) yielded
four candidate cluster members: Kepler-1627, Kepler-1643, KOI-7368,
and KOI-7913.  Given our earlier analysis of Kepler-1627, we focus
here on the latter three.  After analyzing the relevant properties of
Cep-Her (Section~\ref{sec:cluster}), we derive the stellar properties
(Section~\ref{sec:stars}) and validate the planetary nature of each
system using a combination of the Kepler photometry and
high-resolution imaging (Section~\ref{sec:planets}).  We conclude with
a discussion of mini-Neptune size evolution, and point out possible
directions of future work (Section~\ref{sec:disc_conc}).

@@

%
% KOI match numbers from calc_CepHer_group_numbers.py
%
Our fourth and final step was to cross-match the candidate Cep-Her
member list against all known Kepler Objects of Interest.  We used the
Cumulative KOI table from the NASA Exoplanet Archive from 27 March
2022, and also compared against the \texttt{q1\_q17\_dr25} table
\citep{thompson_planetary_2018}.  From the candidate members
with weights exceeding 0.02, this yielded
 yielded 11 were known false positives, 6 ``confirmed'' planets, and 8
 ``candidate'' planets.  
Inspection of the Kepler data validation summaries and Robovetter
classifications for these objects showed whether they were
potentially consistent with being {\it i)} planets, and {\it ii)}
$\lesssim 10^8$ years old, based on the presence of rotational
modulation at the expected period and amplitude \citep[{\it
e.g.},][Figure~9]{rebull_rotation_2020}.  Four objects remained after
this inspection: Kepler-1627, Kepler-1643, KOI-7368, and
KOI-7913.\footnote{These figures
yield an estimate of the size of Cep-Her: if our 4/14
possible matches represent the true positive rate, then
multiplying by the number of stars above our weight threshold
(12{,}436) yields $\approx$3{,}500 stars in the complex.}

@@

We fitted the data as follows.  Given an initial guess for the transit
ephemeris from \citet{thompson_planetary_2018}, we first trimmed the
light curve to a local window around each transit that spanned three
transit durations before and after each mid-transit time.  The
out-of-transit points in each local window were then fitted with a
fourth-order polynomial, which was divided out from the light
curve.  The resulting flattened transits were then fitted with a
transit model that assumed quadratic limb darkening.
The model therefore included 8 free parameters for the transit ($\{P,
t_0, \log R_{\rm p}/R_\star, b, u_1 ,u_2, R_\star, \log g\}$), 2 free
parameters for the light curve normalization and a white noise jitter
($\{\langle f \rangle, \sigma_f \}$), and 5 fixed
parameters for each transit.

@@

One drawback of our approach is that we have fixed 5 implicit
parameters per individual transit to their MAP values to remove the
starspot-induced variability.  An alternative could be to fit the
planetary transits simultaneously with the starspot-induced
variability using a quasiperiodic Gaussian process (GP).  We
explored this approach, but found that it sometimes required fine-tuning
of the hyperparameter priors, otherwise the GP would 
overfit flares, instrumental noise, and any other variability that was not
part of the transit.  This failure mode is pernicious, in that it yields an
ill-founded sense of confidence in a visually clean
fit.  Our model is simpler, and it has the benefit that the white
noise jitter never trades off with any parameter equivalent to a
damping timescale for the coherence of the GP.  It is also
computationally efficient, and it captures the planetary parameters
about which we care the most.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		%    namelist = ['Kepler-1627 A', 'KOI-7368', 'KOI-7913 A', 'KOI-7913 B', 'Kepler-1643']
		%    markers = ['P', 'v', 'X', 'X', 's']
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ages more precise than a factor of
    three are emphasized. The Cep-Her planets are
    Kepler-1643~b ($\square$), KOI-7368~b ($\triangledown$),
    KOI-7913~Ab (X), and Kepler-1627~Ab (+).  
    Interesting trends in the population of young planets currently include
    {\it i)} their large sizes 
    and {\it ii)} the lack of young hot Jupiters.
    The new objects of interest in Cep-Her have normal mini-Neptune sizes
    between 2 and 3\,$R_\oplus$, which is a novelty given their ages.
    Parameters are from the NASA Exoplanet Archive (2022 Apr 5).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

The theoretical expectation is that mini-Neptunes with sizes of 2 to
3\,$R_\oplus$ should be common at ages of $10^7$ to $10^8$ years.
This expectation is tied to inferences about the
initial distributions of planetary core mass, core composition, and
atmospheric mass fraction \citep{owen_evaporation_2017}.  The
Kelvin-Helmholtz cooling timescale, which is tied to the entropy of
the planetary interior once the disk disperses, could also play a
significant role \citep{owen_constraining_2020}.  As an example,
\citet{rogers_unveiling_2021} predicted that given a core-mass
distribution peaked at $\approx$$4$\,$M_\oplus$, an ice-poor rock/iron
core composition, and a typical H/He mass fraction of $\approx$4\%,
there should be a maximum in planet occurrence at 2 to 3\,$R_\oplus$
at times between 10 and 100\,Myr
(their Figure~16).  The models advanced by
\citet{gupta_signatures_2020} and \citet{lee_primordial_2021} agree;
the theoretical differences lie in their explanations
for the radius valley.  If the radius gap is primordial
and created by gas accretion physics, then super-Earths
($<$$1.8$\,$R_\oplus$) would be common as early as $10^7$ years
\citep{lee_primordial_2021}.   The photoevaporation-driven models more
often quote $10^8$ year timescales for production of
atmosphere-stripped super-Earths, while the models with the mass-loss
driven by a slow escape of heat from the core predict longer
$\sim$$10^9$ year timescales (but see \citealt{king_euv_2020}).

@@

From a data-driven perspective, demonstrating that a group of stars
was physically associated at its time of formation is challenging.
While some young groups show kinematic evidence for expansion
\citep{kuhn_kinematics_2019}, many, including Sco-Cen, do not
\citep{wright_kinematics_2018}.  This complicates the feasibility of
deriving kinematic ages through traceback, as
well as through the expansion itself
\citep[see][]{crundall_chronostar_2019}.  A more minimal approach is
that suggested by \citet{tofflemire_2021}: search for coeval,
phase-space neighbors, measure their ages, and determine if they share
a common age.  This approach can demonstrate whether a star is {\it
currently associated} with a set of coeval stars, which is much easier
than determining what the association looked like in the past.  Our
analysis of CH-2 meets the latter standard for the existence of a
$\approx$40\,Myr assocation today.  It would be a worthy exercise for
future work to perform a similar search for coeval phase-space
neighbors on the entire dataset of known exoplanet hosts.  For the
time being, we can offer the anecdotal point that in our experience,
most stars do not have dozens of 40\,Myr neighbors within a
local volume of a few \kms\ and tens of parsecs.

@@

\paragraph{Cep-Her}
Our analysis to date has focused only on portions of Cep-Her
that were observed by Kepler: namely RSG-5, CH-2, and the $\delta$~Lyr
cluster.
The membership and kinematics of the other components shown 
in Figure~\ref{fig:XYZvtang} also deserve attention.
R.~Kerr and collaborators have acquired
{\bf N spectra} from which radial velocities will be derived in their upcoming study, but if the estimate that
Cep-Her has $\approx$3{,}500 stars is correct then far more might be required
to fully untangle the kinematics of the various groups.
Wide-field spectroscopic surveys such as LAMOST ({\bf cite}) or
APOGEE ({\bf cite}) could provide sensitivity to the Li 6708\,\AA\ line,
which would enable a more detailed analysis of its abundance across
FGK stars.
Gaia DR3 may also provide RVS spectra
for some of the brighter F and G dwarfs, which could provide the calcium
infrared triplet as another age indicator.

A number of worthy photometric projects also seem possible
given the new understanding of the complex.
One is asteroseismology of the $\delta$~Sct stars,
using either TESS or Kepler data.
For cases in which the modes are resolved, this might yield
age estimates for subgroups independent from other
approaches.
Other projects could include searches of the Kepler data
for exocomets (CITE Zieba), or for missed planets around the
most rapid rotators.

\paragraph{Exoplanet demographics at early times}
Our main motivation for finding new young planets is to help
benchmark models for planetary evolution.
However demographic analyses of the known planets between $10^7$ and $10^9$ years
(Figure~\ref{fig:age}) have so far been somewhat limited.
Approximately 40 such planets
are now known.
The majority of published cases ($\approx$20) come from
K2, though now $\approx$10 come from Kepler, and $\approx$10 
from TESS.

Given these detections, 
a few reflections regarding the experimental design of any
demographic survey might be helpful.
The first is that the list of target stars is an incredibly important
ingredient, and the best way to compile relevant stars right
now is likely through a combination of automated spatio-kinematic clustering
from Gaia and rotation-period measurement with TESS.
The second is that the planets $<$$3$\,$R_\oplus$ in size
all come from either K2 or Kepler.
So demographic inferences based on TESS
for the time being are limited to 
$4$ to $10$\,$R_\oplus$, close-in to the host stars.  
It seems worthwhile to comparable
the absolute occurrence rate of such planets to those derived from
Kepler (CITE Petigura).
One question that seems like it should be within reach would be to clarify
whether enough young stars have been searched for the dearth of
young hot Jupiters shown in Figure~\ref{fig:age} to be significant.
Since the hot Jupiter occurrence rate is strongly dependent on stellar
mass and metallicity (CITE), particular care would be needed to select
a sample of FGK dwarfs for the measurement, likely going out
to distances of $\approx$500\,pc to get enough stars.
The major sources of stars in the youngest age bins would
need to include Sco OB2, Cep-Her, and Orion, among others.
For studies of how mini-Neptune sizes evolve, the combined K2 and Kepler
dataset might be the better primary source.
Though the selection function is more stringent, for a given star
Kepler acquired $\sim$100$\times$ more photons.  Given the
star-count limited nature of a cluster-based exoplanet demographic
survey, every star counts.

@@

We have showed that Kepler-1643~b, KOI-7368~b, and KOI-7913~Ab
are 40 to 50 million years old, and that each signal
is most likely planetary.  The evidence for the planetary
interpretation comes from an application of \texttt{VESPA} to the
Kepler data, alongside new adaptive optics imaging from NIRC2.  The
validity of the \texttt{VESPA} framework rests on the premise that
non-astrophysical false positives, including false alarms and known
neighboring eclipsing binaries, can be rejected.  Kepler-1643 and
KOI-7368 both pass all but one of the canonical vetting checks: the
check for centroid offsets between the in and out-of-transit phases.
For both cases, we have argued the weak observed shifts seem to be
caused by starspot-induced variability in specific quarters
shifting the stellar center-of-light.
In addition, our imaging rules out companions stars with the necessary
brightness and position to explain the reported shifts.

@@

The spatio-kinematic argument for the youth of KOI-7368 and
KOI-7913 is weaker because they are in an association of stars, CH-2,
that is more diffuse.  For KOI-7913, stronger indicators of its age
come from its binary.  Both stellar components in KOI-7913
have isochronal ages consistent with $40$\,Myr.
Both components also show H$\alpha$ in emission, which for
the $\approx$K6V primary is a strong indicator that the star is
$\lesssim$100$\,$Myr old.  For KOI-7368, which is slightly more
massive, the Li 6708\AA\ EW measurement and stellar rotation period
are more constraining, and provide independent verification of the
star's youth.

The astrophysical significance of these somewhat detailed considerations
is that planets $\sim$2 Earth radii in size exist at ages of 40 million years.
It will be interesting to continue the push down to smaller planetary
sizes at comparable ages -- the planetary detections we have
presented are well above the average detection significance of Kepler 
planets.  There may well still be room at the bottom.
